```{r data generation, echo = FALSE, results = "hide"}
pacman::p_load(tidyverse, exams)
## DATA GENERATION
n = 10
mu <- sample(c(125, 200, 250, 500, 1000), 1)
y <- round(rnorm(n, mean = mu * runif(1, min = 0.9, max = 1.1),
           sd = mu * runif(1, min = 0.02, max = 0.06)))

## QUESTION/ANSWER GENERATION
mean_value <- round(mean(y), digits = 2)

list_of_answers <- c(paste0(mean(y),"correct"),median(y), sum(y), mean(y[1:5]))
list_of_correct <- c(TRUE, FALSE, FALSE, FALSE)

order_of_questions <- sample.int(4,4,replace = FALSE)

list_of_answers <- list_of_answers[order_of_questions]

list_of_correct <- list_of_correct[order_of_questions]

```

Question
========

A farmer is trying calculate the average weight of his pigs before taking them to market. He weighs a sample of $10$ pigs from the herd and gets the following weights in kilograms:

$`r y`$

What is the value of the mean pig weight:

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(list_of_answers)
```

Solution
========
The mean of the pig weights is:

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(list_of_correct, "TRUE", "FALSE"), markup = "markdown")
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(list_of_correct, single = TRUE)`
exname: t statistic