```{r data generation, results='hide', echo=FALSE}
pacman::p_load(tidyverse, gt, exams)
rand_probs <- seq(from = 0, to= 1, by = 0.01)

ks <- sample(rand_probs,4)

while(sum(ks) != 1){
  ks <- sample(rand_probs,4)
}
data <- data.frame(k = 1:4, 
                   prob = c(ks))

pmf <- data |> 
  gt() |> 
  cols_label(prob = "P(X = k)")

xp <- c()
for (i in 1:4){
  xp[i] <- data$k[i] * data$prob[i]
}
sol <- round(sum(xp),2)

```
Question
===================
Calculate the mean of the following probability distribution. Give your answer to 2 decimal places

```{r showtable, echo=FALSE}
pmf
```


Solution
=============
To find the mean of the probability distribution, multiply each possible value by its probability, then add all the products:
$$E[X] = \sum^{\text{all }k} k_i P(X=k)$$
which can be written as
```{r calculation, echo=FALSE}
print(paste0(data$k[1], " * ", data$prob[1], " + ", data$k[2], " * ", data$prob[2], " + ", data$k[3], " * ", data$prob[3], " + ", data$k[4], " * ", data$prob[4]))
```
Therefore rounded to 2 decimal places is `r sol`

Meta-information
================
extype: num
exsolution: `r fmt(sol, 2)`
extol: 0.01
exname: calculate-valid-pmf

