```{r data generation, echo=FALSE, results='hide'}
num_dogs <- sample(20:30, 1)

# Dog owners: mostly unbothered
dog_judgment <- sample(
  x = 1:6,
  size = num_dogs,
  replace = TRUE,
  prob = c(0.10, 0.25, 0.30, 0.20, 0.10, 0.05)
)

# Cat owners: deeply judged
cat_judgment <- sample(
  x = 3:10,
  size = num_dogs,
  replace = TRUE,
  prob = c(0.05, 0.05, 0.10, 0.15, 0.20, 0.20, 0.15, 0.10)
)

data <- data.frame(
  dog_judgment = dog_judgment,
  cat_judgment = cat_judgment
)


choices <- character(4)
choices[1] <- "$H_0$: The distribution of judgement scores is the same for cat owners and dog owners, \n $H_a$: The distribution of judgement scores for cat owners is different to dog owners."

choices[2] <- "$H_0$: The mean judgement score of cat owners equals the mean judgement score of dog owners.\n $H_a$: The mean judgement score of cat owners is greater than the mean judgement score of dog owners."

choices[3] <- "$H_0$: Cat owners and dog owners feel equally judged by their pets. \n $H_a$: Cat owners feel more judged by their pets than dog owners, on average."

choices[4] <- "$H_0$: The variance of judgement scores is the same for cat owners and dog owners. \n $H_a$ : Cat owners have higher judgement scores because cats are more judgmental animals."


sol <- c(T, F, F, F)
```

Question
===================
A behavioural science lab wants to study perceived judgement from pets. They recruit pet owners and ask them to rate, on a 1-10 scale, how judged the owners feel when their pet watches them eat dropped food from the floor. This dataset collected has 2 variables:

1.  Scale of judgement:
1 = "pure unconditional love"
10 = "you have severely disrespected my ancestors" 

2.  Type of pets: dogs and cats

The final dataset looks like:
```{r show data, echo=FALSE}
head(data)
```


The researcher decides to use a Mann-Whitney U test for this study.

What are the appropriate null and alternative hypotheses for this study?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```




Solution
======================
Mann–Whitney U tests whether the distributions differ, not a specific direction. There should not be a mention of mean/variance as well. 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```




Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: mann-whitney-null-and-alt-hyp
exshuffle: TRUE


