```{r data generation, echo=FALSE, results='hide'}
choices <- character(5)

choices[1] <- "The sample mean is insensitive to outliers and skewness."

choices[2] <- "The sample mean and standard deviation are insensitive to outliers and skewness."

choices[3] <- "The sample mean and standard deviation are both sensitive to outliers and skewness."

choices[4] <- "The sample mean is insensitive to outliers and skewness, but the sample standard deviation is not."

choices[5] <- "The sample mean and sample median are both sensitive to outliers and skewness."

sol <- c(FALSE, FALSE, FALSE, FALSE, TRUE)


```

Question 
===============
Which of the following statements is true?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
================
The sample mean is sensitive to outliers because extreme values can pull the mean toward them, which results in the sample mean not representing the "central"/"typical" value in the data. 


The sample standard deviation is also sensitive to outliers, as it involves the square of the differences from the mean. Outliers increase these differences, which will result in a larger standard deviation. 



The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "True", "False"), markup = "markdown")
```




Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: affected by skewness
exshuffle: TRUE
