```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
choices <- character(4)
choices[1] <- "To compare the means of two independent groups"
choices[2] <- "To compare the variances of multiple groups"
choices[3] <- "To test whether at least one group mean differs among three or more groups"
choices[4] <- "To test the relationship between two continuous variables"


sol <- c(FALSE, FALSE, TRUE, FALSE)


```

Question
==============
What is the primary purpose of a one-way ANOVA?


```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
==================
A one-way ANOVA tests whether all group means are equal across three or more independent groups. It does not identify which groups differ, or how many groups differ, only that at least one difference exists. 



The correct answer is :
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "True", "False"), markup = "markdown")
```




Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: anova-one-way-purpose
exshuffle: TRUE