```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)

choices[1] <- "Both main effects must be significant"
choices[2] <- "The effect of one factor depends on the level of the other factor"
choices[3] <- "The factors are statistically independent"
choices[4] <- "There is no main effect of either factor"

sol <- c(FALSE, TRUE, FALSE, FALSE)

```

Question
=================
What does a significant interaction between two factors in a two-way ANOVA imply?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```




Solution
===================
An interaction means the effect of one factor changes depending on the level of the other factor, making main effects alone potentially misleading.

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "True", "False"), markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(correct, single = TRUE)`
exname: anova-two-way-interaction-means
exshufflr: TRUE




