```{r data generation, echo = FALSE, results = "hide"}
sample <- rnorm(14, mean = 50, sd = 20)
sample <- round(sample,0)
length <- length(sample)
sorted <- sort(sample)
sol <- round(median(sample),1)
```

Question
===============
Calculate the median for the following sample: 

$$`r sample`$$
Please give your answer to 1 decimal place. 



Solution
========
We obtain the median of a sample by first arranging the data points from smallest to largest

$$ `r sorted`$$

then take the central number. If there are 2 numbers in the middle, the median is the average of those 2 numbers. 
If the size of the data, $n$, is off, the median is the value at position $p$, where

$$p = \frac{n+1}{2}$$

If $n$ is even then the median is the average/mean of the values at positions $p$ and $p+1$ where
$$p = \frac{n}{2} $$

In R, the data can be entered using:
```{r, echo = FALSE}
cat('sample=c(',paste(sample, collapse=','), ')\n', sep = '')

```


Then you can compute the median like so:
 
```{r}
median(sample)
```
 
which rounded to one decimal place is `r sol`.


Meta-information
================
extype: num
exsolution: `r fmt(sol, 1)`
extol: 0.01
exname: calculate sample mean
