```{r data generation, echo=FALSE, results='hide'}
rand_num <- sample(35:100, 1)
rand_mean <- sample(60:85, 1)
rand_sd <- sample(1:10, 1)
sample_mean <- rand_mean
sample_sd <- rand_sd
num <- rand_num
se <- rand_sd/sqrt(rand_num)
t <- 2.064
lb <- round(rand_mean - t * se,2)
ub <- round(rand_mean + t*se,2)

choices <- character(4)
choices[1] <- paste0("(", lb, ", ", ub, ")")
choices[2] <- paste0("(", round(rand_mean - t * rand_sd/rand_num,2), ", ", round(rand_mean + t * rand_sd/rand_num,2), ")")

choices[3] <- paste0("(", rand_mean, " $\\pm$ " , round(se,2), ")")
choices[4] <- paste0("(", round(rand_mean - t * rand_sd^2/rand_num,2), ", ", round(rand_mean + t * rand_sd^2/rand_num,2), ")")

sol <- c(T, F, F, F)

```



Question
===================
A random sample of $n = $`r rand_num` high school students has a sample mean math test score of $\bar{x} = $ `r rand_mean`, with a sample standard deviation of $\sigma = $ `r rand_sd`. 

Assume the population distribution is approximately normal, and you may use the 95% critical value to be $t^* = 2.064$. 

Calculate the 95% confidence interval for the true mean math score. Round your answer to 2 decimal places. 

```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```



Solution
==========
The 95% Confidence Interval can be calculated using the formula:
$$\bar{x} \pm 2.064 \times \frac{\sigma}{\sqrt{n}}$$
In R, this can be done by substituting $\bar{x}=$ `r sample_mean`, and $\sigma=$ `r sample_sd`
```{r, echo=TRUE,}
lower_bound <- sample_mean -2.064* sample_sd/sqrt(num)
upper_bound <- sample_mean +2.064* sample_sd/sqrt(num)
```

```{r, echo = FALSE, results='asis'}
lower_bound  <- round(sample_mean -2.064* sample_sd/sqrt(num),2)
upper_bound <- round(sample_mean +2.064* sample_sd/sqrt(num),2)

paste0("(", lower_bound, ", " ,upper_bound, ")")
```


The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: calculate-95-CI-t-test
exshuffle: TRUE
