```{r data generation, echo=FALSE, results='hide'}
num <- sample(40:70, 1)
sample_mean <- sample(seq(20, 40, by = 0.1),1)
sample_sd <- sample(seq(1, 10, by = 0.01),1)

X <- round(sample_mean -1.96* sample_sd/sqrt(num),2)
Y <- round(sample_mean +1.96* sample_sd/sqrt(num),2)


choices <- character(8)
choices[1] <- paste0("X = ", X)
choices[2] <- paste0("Y = ", Y)
choices[3] <- paste0("Y = ", X)
choices[4] <- paste0("X = ", Y)
choices[5] <- paste0("X = ", round(sample_mean -1.96* sample_sd^2/sqrt(num),2))
choices[6] <- paste0("X = ", round(sample_mean -1.96* sample_sd/num,2))
choices[7] <- paste0("Y = ", round(sample_mean +1.96* sample_sd^2/sqrt(num),2))
choices[8] <- paste0("Y = ", round(sample_mean +1.96* sample_sd/num,2))

sol <- c(T,T, F,F,F,F,F,F)

```



Question
==================
`r num` wombats are randomly selected and their weight is measured in kilograms. The sample mean is $\bar{x}=$ `r sample_mean`, and the population standard deviation is known to be $\sigma=$ `r sample_sd`. You may assume $Z^* = 1.96$. Please give your answer to 2 decimal places. 

Assuming the weight of wombats is normally distributed, please find the value of $X$ and $Y$ in the following sentence:

"The 95% confidence interval for the true mean weight of wombats (in kilograms) is $(X,Y)$"

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```


Solution
==========
X and Y can be calculated using the formula:
$$\bar{x} \pm 1.96 \times \frac{\sigma}{\sqrt{n}}$$
In R, this can be done by substituting $\bar{x}=$ `r sample_mean`, and $\sigma=$ `r sample_sd`
```{r, echo=TRUE,}
X <- sample_mean -1.96* sample_sd/sqrt(num)
Y <- sample_mean +1.96* sample_sd/sqrt(num)
```

```{r, echo = FALSE, results='asis'}
X <- round(sample_mean -1.96* sample_sd/sqrt(num),2)
Y <- round(sample_mean +1.96* sample_sd/sqrt(num),2)

paste0("X = ", X)
paste0("Y = ", Y)
```


The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol)`
exname: calculate-95-CI-Z-test
exshuffle: TRUE
