```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(exams, tidyverse)
rand_mean<- sample(150:200, 1)
rand_sd<- sample(1:10, 1)
ques <- sample(160:210,1)
choices <- character(4)
choices[1] <- paste0("`pnorm(", ques, ", mean = ", rand_mean, ", sd = ", rand_sd, ")`")
choices[2] <- paste0("`1 - pnorm(", ques, ", mean = ", rand_mean, ", sd = ", rand_sd, ")`")
choices[3] <- paste0("`qnorm(", 0.95, ", mean = ", rand_mean, ", sd = ", rand_sd, ")`")
choices[4] <- paste0("`dnorm(", ques, ", mean = ", rand_mean, ", sd = ", rand_sd, ")`")


sol <- c(FALSE, T, F, F)
```


Question
================
The heights of students, $X$, are normally distributed with mean `r rand_mean`, and standard deviation `r rand_sd`. Which R command calculates $P(X >$ `r ques` $)$


```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
==============
`pnorm()` calcultes the left tail probability $P(X\leq x)$, therefore to calculate $P(X > x ) = 1- P(X\leq x) = 1-$ `pnorm()`
 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single=TRUE)`
exname: calculate-right-tail-prob
exshuffle: TRUE
