```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(exams, tidyverse)
choices <- character(4)
explain <- character(4)
choices[1] <- "`mean(x) - mean(y) + c(-1,1) * 1.96 * sqrt(sd(x)^2 + sd(y)^2)`"
choices[2] <- "`mean(x) - mean(y) + c(-1,1) * 1.96 * sqrt(sd(x)^2/length(x) + sd(y)^2/length(y))`"
choices[3] <- "`t.test(x, y)$conf.int`"
choices[4] <- "`mean(x - y) + c(-1,1) * 1.96 * sd(x - y)`"


explain[1] <- "This is missing the division of sample sizes"
explain[3] <- "This calculates a t-distribution based interval, instead of a normal-theory"
explain[4] <- "This interval is for paired samples, where `x` and `y` are dependent. "

sol <- c(FALSE,TRUE,FALSE,FALSE)
```



Question
==============
Suppose you have two independent samples `x` and `y`. Which R command below computes a 95% normal-theory confidence interval for the difference of means? 





```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```


Solution
=================
The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), explain, markup = "markdown")
```


The standard error for the difference of two independent means is:
$$\sqrt{\frac{s_x^2}{n_x} + \frac{s_y^2}{n_y}}$$




Meta-information
================
exname: calc-CI-2-vars
extype: schoice
exsolution: exsolution: `r mchoice2string(sol, single = TRUE)`
