```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
choices <- character(4)
choices[1] <- "One-sample t-test"
choices[2] <- "Two-sample t-test"
choices[3] <- "Chi-square test"
choices[4] <- "Mann-Whitney test"

sol <- c(F, F, T, F)

```


Question
===================
A researcher records whether university students own a pet (Yes/No), and their study mode (Online/On-campus). Which test is most appropriate to assess whether pet ownership is associated with study mode?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```




Solution
======================
Both variables are categorical, and the goal is to test for association, the chi-square test is appropriate in this case. 
The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```




Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: chi-square-when-to-use
exshuffle: TRUE

