```{r data generation, echo=FALSE, results='hide'}
rand_sd <- sample(5:20, 1)
num_sample <- sample(35:100, 1)

ans <- round(rand_sd/sqrt(num_sample),3)
choices <- c()
choices[1] <- rand_sd/sqrt(num_sample)
choices[2] <-  rand_sd/num_sample
choices[3] <- rand_sd^2/num_sample
choices[4] <- (rand_sd/num_sample)^2

choices <- round(choices,3)
sol <- choices== ans
```
Question
===============

We want to estimate a population mean with a Normal distribution with a known population standard deviation of `r rand_sd`. Given that `r num_samples` samples are taken, what is the standard error?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```


Solution
==========
In the case of a population mean for a Normal distribution with a known population standard deviation, we have the standard deviation calculated by:
$$\frac{\sigma}{\sqrt{n}}$$
where $\sigma$ is the standard deviation, and $n$ is the number of samples taken.

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single=TRUE)`
exname: CI-calculate-std-error
exshuffle: TRUE
