```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)
choices[1] <- "The population standard deviation is known and the sample size is large"
choices[2] <- "The population standard deviation is unknown and estimated from the sample"
choices[3] <- "The population is non-normal"
choices[4] <- "The sample mean is unknown"
sol <- c(F, T, F, F)
```


Question
================
Which of the following situations require using the t-distribution to find the critical value for a confidence interval? 
```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```


Solution
=================
A t-interval is used when the population standard deviation $\sigma$ is unknown and replaced by the sample standard deviation $s$.

The correct answer is 
```{r answerlist, echo=FALSE, results='asis'}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(correct, single = TRUE)`
exname: CI-when-to-use-t-dist
exshuffle: TRUE


