```{r data generation, echo=FALSE, results='hide'}

choices <- character(4)
choices[1] <- "Interval A will be wider than Interval B"
choices[2] <- "Interval B will be wider than Interval A"
choices[3] <- "Both intervals have the same width"
choices[4] <- "The width depends only on the sample mean"


sol <- c(F, T, F, F)
```

# Question

Two confidence interval for the same population mean are constructed from the same data:

1.  Interval A: 90% confidence interval
2.  Interval B: 95% confidence interval

Which of the following statements is correct? 

```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```


Solution
=================
Higher confidence require a larger critical value, which leads to a wider interval. This can be checked using 
```{r showsteps, echo = TRUE, results='hide'}
crit_value_0.9 <- qnorm(1-(1-0.9)/2, mean = 0, sd = 1)
crit_value_0.95 <- qnorm(1-(1-0.95)/2, mean = 0, sd = 1)
```

```{r}
cat("The critical value for 90% confidence interval is", crit_value_0.9, "\n")
cat("The critical value for 95% confidence interval is", crit_value_0.95, "\n")
```

The correct answer is 
```{r answerlist, echo=FALSE, results='asis'}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(correct, single = TRUE)`
exname: comparing-crit-value-CI
exshuffle: TRUE



