```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(tidyverse, exams)

choices <- character(4)
choices[1] <- "{H, T}, categorical"
choices[2] <- "{0,1}, numeric"
choices[3] <- "{0,1,...,30}, numeric"
choices[4] <- "{0-30}, continuous" 
sol <- c(FALSE, FALSE, TRUE, FALSE)


```

Question 
================
A coin is flipped $n = 30$ times. The variable recorded is the number of heads obseerved. 
Which correctly describes the sample space and the variable type?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```

Solution
====================
The variables is a count of number of heads, so it is numeric discrete with values from 0 to $n$. 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: identify-sample-space-and-variable-type-coin
exshuffle: TRUE






