```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
sample_size <- sample(size = 1,c(1:100))

subjects_choices <- character(4)
variables_choices <- character(4)

subjects_choices[1] <- "Subjects: screen time"
subjects_choices[2] <- "Subjects: participants"
subjects_choices[3] <- "Subjects: number of hours of sleep"
subjects_choices[4] <- "Subjects: gender"
sol_choices <- c(FALSE, TRUE, FALSE, FALSE)

variables_choices[1] <- "Variables: participants"
variables_choices[2] <- "Variables: screen time"
variables_choices[3] <- "Variables: number of hours of sleep" 
variables_choices[4] <- "Variables: gender"
sol_variables <- c(FALSE, TRUE, TRUE, TRUE)

choices <- c(subjects_choices, variables_choices)
sol <- c(sol_choices, sol_variables)


```


Question 
================
A researcher collects data from $n = $`r sample_size` participants. For each participant, the folllowing variables are recorded: 
- daily screen time (hours)
- number of hours of sleep (0-12)
- gender (Male, Female, Non-binary, Prefer not to say)

What are the subjects and variables in this dataset? 
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```




Solution
================
The subjects are the observational units (participants)

The variables are the measurements recorded for each participants.

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol)`
exname: identify-subjects-and-variables


