```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)

choices[1] <- "95% of the data lies inside the interval"
choices[2] <- "The interval contains the sample mean 95% of the time"
choices[3] <- "95% of the intervals constructed using this method will contain the true mean"
choices[4] <- "There is a 95% chance the interval is correct"
sol <- c(F, F, T, F)
```

Question
=================
What does the "95%" in a 95% Confidence Interval mean?

```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```



Solution
==================
A confidence interval is based on a procedure, not on probability statements about a single, already-computed interval.

If you repeatedly took random samples from the same population, and constructed a confidence interval from each sample using the same method, then about 95% of those intervals would contain the true population mean.


The correct answer is 
```{r answerlist, echo=FALSE, results='asis'}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(correct, single = TRUE)`
exname: interpret-the-95-of-CI
exshuffle: TRUE


