```{r data generation, echo=FALSE, results='hide'}
conf_int <- sample(90:99, 1)
conf_int_2 <- 100-(100-conf_int)*2
rand_mean <- rnorm(1, mean = 50, sd = 5)
lb <- round(rand_mean - 1.959964 * 50/sqrt(50),2)
ub <- round(rand_mean + 1.959964 * 50/sqrt(20),2)


choices <- character(4)
choices[1] <- paste0("We are ", conf_int, "% confident that the true mean wingspan of seagulls lies between ", lb," and ", ub, " centimetres.")

choices[2] <- paste0("We are ", conf_int_2, "% confident that the true mean wingspan of seagulls lies between ", lb," and ", ub, " centimetres.")

choices[3] <- paste0("We are ", conf_int, "% confident that the sample mean wingspan of seagulls lies between ", lb," and ", ub, " centimetres.")

choices[4] <- paste0("The probability that the true mean wingspan of seagulls lies between ", lb, " and ", ub, " millimetres is ", conf_int/100, ".")

sol <- c(T, F, F,F)

```

Question
===============
Suppose the `r conf_int`% confidence interval for the population mean wingspan of seagulls (measured in centimetres) is (`r lb`, `r ub`). What is the correct interpretation of this confidence interval?
```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```


Solution
=================
The confidence level is interpreted by:
We are `CI level` confident that the true `parameter` of `population` lies between `lower` and `upper` `units`.

The correct answer is 
```{r answerlist, echo=FALSE, results='asis'}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(correct, single = TRUE)`
exname: interpret-rand-CI
exshuffle: TRUE


