```{r data generation, echo=FALSE, results='hide'}
n <- 20
data <- rnorm(n, mean = 3, sd = 1)
upper <- round(mean(data) + 1.96*1/n, 2)
lower <- round(mean(data) - 1.96*1/n, 2)



choices <- character(4)
choices[1] <-  paste("95% of newborns in this hospital weigh between", lower, "kg and", upper,"kg.")
choices[2] <- paste("There is a 95% chance that the true mean newborn weight is between",lower, "and", upper, "kg.")
choices[3] <- "If we repeated this sampling process many times, about 95% of the intervals we compute would contain the true mean."
choices[4] <- paste("The sample mean definitely lies between", lower, "and", upper, "kg.")

sol <- c(FALSE,FALSE,TRUE,FALSE)

```




Question
===============
A 95% confidence interval for the mean weight of newborns in a hospital is (`r lower`kg, `r upper`kg). Which is the correct interpretation?



```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```



Solution
==================
A 95% CI means that the method used will capture the true mean in about 95% of repeated samples—not that 95% of individuals fall within the interval or that there is a literal 95% probability about this specific interval.

The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```






Meta-information
================
exname: interpret-CI
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE
