```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)
explain <- character(4)

choices[1] <- "The treatment definitely has no effect."
choices[2] <-  "There is evidence that Treatment increases blood pressure."
choices[3] <- "The treatment effect could be negative, zero, or positive based on this interval."
choices[4] <- "90% of patients had blood pressure changes between −2 and 5 mmHg"

sol <- c(FALSE,FALSE,TRUE,FALSE)
```

Question
==================
A researcher reports a 90% CI for the difference in mean blood pressure between Treatment and Control as (−2 mmHg, 5 mmHg). What conclusion is reasonable?


```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```


Solution
==============
Because the interval includes 0, the data are consistent with a negative, zero, or positive effect. It does not show “no effect,” nor does it imply anything about 90% of individual blood pressure measurements.


The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```




Meta-information
================
exname: interpret-CI-2
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE
