```{r data generation, results='hide', echo=FALSE}
data <- data.frame(attention_span = rnorm(120, mean = 60, sd = 10), 
                   treatment = rep(c("caffeine", "placebo"), each = 60))
data$attention_span[data$treatment == "caffeine"] <- data$attention_span[data$treatment == "caffeine"] + rgamma(60, shape= 10, rate = 1)

data$attention_span[data$treatment == "placebo"] <- data$attention_span[data$treatment == "placebo"] - rgamma(60, shape= 5, rate = 1)

plot1 <- data |> ggplot(aes(x = treatment, y = attention_span, fill = treatment)) + geom_boxplot() + theme_bw() + theme(legend.position = "none") + labs(x = "Treatment", 
          y = "Attention Span")

choices <- character(4)

choices[1] <- "Caffeine causes faster reaction time"
choices[2] <- "The caffeine group tends to have faster reaction time"
choices[3] <- "The placebo is ineffective"
choices[4] <- "Reaction time is normally distributed"

sol <- c(FALSE, TRUE, FALSE, FALSE)
```

Question
====================
A student wants to compare attention span for a caffeinated group and a placebo group. They conducted the experiment for a total of 120 students. A side-by-side boxplot is then used to compare the recorded results. 
```{r showplot, echo=FALSE}
plot1
```
Which interpretation is most appropriate? 

```{r showplot, echo=FALSE, results='asis'}
left_skew_plot
```

What does this plot suggests?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```




Solution
=======================
Boxplots show tendencies, but does not indicate causation. 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single=TRUE)`
exname: interpret-boxplot-caffeine
exshuffle: TRUE

