```{r data generation, echo=FALSE, results='hide'}
mean <- sample(120:135,1)
sd <- sample(10:20,1)

lb <- round(mean-2.064*sd/sqrt(sample(100:120,1)),2)
ub <- round(mean+2.064*sd/sqrt(sample(100:120,1)),2)

choices <- character(4)
choices[1] <- paste0("There is a 95% probability that the true mean loudness of cockatoo shrieks lies between ", lb, "dB and ", ub ,"dB")
choices[2] <- paste0("95% of cockatoos make shrieks that are between ", lb, "dB and ", ub ,"dB loud")
choices[3] <- paste0("We are 95% confident that the true mean loudness of cockatoo shrieks lies between ", lb, "dB and ", ub ,"dB")

choices[4] <- paste0("The true mean loudness of cockatoo shrieks is ", round(0.5*(lb + ub),2), "dB")

sol <- c(F, F, T, F)

```



Question 
==================
Suppose the 95% confidence interval for the mean loudness of shrieks cockatoos make is (`r lb`, `r ub`) decibels (dB). 
Which of the following is the correct interpretation? 

```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```


Solution
=================
The confidence level is interpreted by:
We are `CI level` confident that the true `parameter` of `population` lies between `lower` and `upper` `units`. Confidence interval refers to the method, not the probability of a fixed parameter. 

The correct answer is 
```{r answerlist, echo=FALSE, results='asis'}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(correct, single = TRUE)`
exname: interpret-95-CI
exshuffle: TRUE


