```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(tidyverse, exams)

n = 50
bp <- rnorm(n, mean = 90, sd = 20)
lower <- round(mean(bp) - 1.96*sd(bp)/n,3)
upper <- round(mean(bp) + 1.96*sd(bp)/n,3)



choices <- character(4)
choices[1] <- paste("All the blood pressure observed falls between", lower, "and", upper, "mmHg.")
choices[2] <- paste("95% of future blood pressure measures would be between", lower, "and", upper, "mmHg.")
choices[3] <- paste("We are 95% confident that all of the observed blood pressure falls betwen", lower, "and", upper, "mmHg.")
choices[4] <- paste("In 95% of repeated samples, the calculated condfidence interval,(",lower, ",", upper,") would contain the true population mean.")


sol <- c(FALSE, FALSE, FALSE, TRUE)

explain <- character(4)
explain[1] <- "the confidence interval does not imply that all observed values fall within it. It only applies to the population parameter, not the individual data points."

explain[2] <- "the confidence interval refers to where the true population mean is likely to fall, not the distribution of future individual measurements."

explain[3] <- "the confidence interval applies to the population mean, not individual observations. It doesn't guarantee that all observed values lie within the interval."

```

Question
===================
Researchers want to calculate the mean blood pressure of all the staff at Adelaide University. 50 staff members were sampled, and the confidence interval (CI) was calculated to be (`r `lower` mmHg, `r `upper` mmHg). 

Which conclusion is correct?

```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```





Solution
================
The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"),explain, markup = "markdown")
```




Meta-information
================
exname: interpret-CI-2
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE
