```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(exams, tidyverse)
rand_mean<- sample(150:200, 1)
rand_sd<- sample(1:10, 1)
ques <- sample(seq(0.1, 1, by = 0.1),1)
questext <- paste0("`qnorm(", ques, ", mean = ", rand_mean, ", sd = ", rand_sd,")`")
choices <- character(4)

choices[1] <- paste0("Probability of observing ", rand_mean)
choices[2] <- paste0("The ", ques*100, "th percentile")
choices[3] <- "A random sample"
choices[4] <- "The standard deviation"
```


Question
================
The heights of students, $X$, are normally distributed with mean `r rand_mean`, and standard deviation `r rand_sd`. 

What does this R code return ?
`r questext`


```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
==============
`qnorm()` returns the value corresponding to the given cumulative probability. 
 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single=TRUE)`
exname: interpret-quantile-qnorm
exshuffle: TRUE
