```{r data generation, echo=FALSE, results='hide'}

choices <- character(4)
choices[1] <- "Coffee causes increased alertness in everyone"
choices[2] <- "The results suggest an association but may not generalise"
choices[3] <- "The results prove causation" 
choices[4] <- "The study has no limitations"

sol <- c(FALSE,TRUE,FALSE,FALSE)

```

Question
=======================
A study of 25 volunterrs finds that people who drink coffee report higher alertness than those who do not. 

Which statement is the most appropriate interpretation? 

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
==============
Small samples and observational designs require careful interpretation and disclaimers.

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: interpretation-coffee
exshuffle: TRUE
