```{r data generation, echo=FALSE, results='hide'}

data <- data.frame(left_skewed_data = rbeta(120, shape1 = 14, shape2 = 2)*100) 

left_skew_plot <- ggplot(data, aes(x = left_skewed_data)) + geom_histogram(fill = "lightgreen", colour = "black") + theme_bw() + labs(x = "Percentage of students passing a course (%)")

choices <- character(4)
choices[1] <- "Most of the courses are very hard to pass, but some are easier"
choices[2] <- "A few courses are very hard to pass, but most are easier"
choices[3] <- "All the courses are equally easy to pass"
choices[4] <- "The courses are spread evenly across all levels of difficulty"

sol <- c(FALSE, TRUE, FALSE, FALSE)

```

Question
========================
The plot below shows a histogram of the percentage of students passing a course in univeristy over the 120 courses that the university offers. For a course to be easy, the percentage of passing should be high.
```{r showplot, echo=FALSE, results='asis'}
left_skew_plot
```

What does this plot suggests?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```




Solution
=======================
The plot has a long left tail, which is left skewed. This means that most of the courses are easier to pass. However, there are still a few courses at the left tail of the plot, indicating there are some courses harder to pass than others. 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single=TRUE)`
exname: interpret-left-skew-from-plot
exshuffle: TRUE

