```{r data generation, echo = FALSE, results='hide'}

choices <- character(4)
choices[1] <- "One-sample t-test"
choices[2] <- "One-way ANOVA"
choices[3] <- "Chi-square test"
choices[4] <- "Kruskal-Wallis test"

sol <- c(F, F, F, T)
```

Question
================
A researcher wants to compare the stress scores of participants across 4 independent treatment groups. The stress scores are continuous but heavily skewed, and normality assumptions are not met. 

Which test is most appropriate?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```

Solution
======================
The Kruskal-Wallis test is a non-parametric alternative to one-way ANOVA. It's used when comparing three or more independent groups with non-normal data
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: kw-when-to-use
exshuffle: TRUE



