```{r data generation, echo=FALSE, results='hide'}
ans <- character(5)

ans[1] <- "Observation comes from a binomial distribution."
ans[2] <- "Linearity."
ans[3] <-  "Constant spread of residuals."
ans[4] <- "Normality of residuals."
ans[5] <- "Independence of residuals."
sol <- c(TRUE,FALSE,FALSE,FALSE, FALSE)


```

Question
==================
Which of the following is not an assumption for a linear regression model?

```{r questionlist, echo=FALSE, results = "asis"}
answerlist(ans, markup = "markdown")
```


Solution
=================
The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```

The 4 assumptions for a linear model are:
-    Independent (no correlation between residuals)
-    Linearity (linear relationship between variables)
-    Normality (residuals are normally distributed)
-    Homoscedasticity/Constant spread (variance of the residuals should be constant)

Meta-information
================
exname: lm-assumptions
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE