```{r data generation, echo = FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
n <- sample(30:100, 1)
# Daily study time (hours)
study_time <- runif(n, min = 0, max = 8)

# True relationship parameters
beta_0 <- 2.0   # baseline GPA
beta_1 <- 0.4   # GPA increase per study hour

# Generate GPA with noise
gpa <- beta_0 + beta_1 * study_time + rnorm(n, mean = 1, sd = 1)

# Keep GPA within 0–7
gpa <- pmin(pmax(gpa, 0), 7)

# Final dataset
data <- data.frame(
  study_time = study_time,
  gpa = gpa
)
data <- round(data,3)

model <- lm(gpa ~ study_time, data = data)
int <- round(model$coefficients[1],5)
slope <- round(model$coefficients[2],5)

choices <- character(4)

choices[1] <- "$H_0: \\beta_0 = 1$, \n $H_a: \\beta_0 \\neq 1$"
choices[2] <- "$H_0: \\beta_1 = 0$, \n $H_a: \\beta_1 \\neq 0$"
choices[3] <- "$H_0: \\mu_1 = 0$, \n $H_a: \\mu_1 \\neq 0$"
choices[4] <- "$H_0: \\beta_0 = 0$, \n $H_a: \\beta_0 \\neq 0$"
sol <- c(F, F, F, T)

```

Question
===============
A researcher wants to know if daily study time (hours) actually has an effect on students final GPA score (from 0 to 7). They conducted a study with `r n` students, and recorded the students' daily study time and final GPA score. The dataset they collected looks like:
```{r showdata, echo=FALSE}
head(data)
```
The linear regression model is then fitted, the results are shown below:
```{r}
summary(model)
```
The researcher theorises that, if students don't study at all, they will fail all their courses and get 0 GPA. Which of the following hypotheses are appropriate for testing this theory
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```

Solution
======================
In a linear regression model, the regression equation is displayed as:
$$y = \beta_0 + \beta_1x$$
where $y$ is the response variable (GPA) and $x$ is the indpendent variable (study hours). The intercept term ($\beta_0$) represents the expected GPA when study time is 0. To test whether students who do not study at all are expected to have a GPA of 0, we test whether the intercept equals zero.

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: lm-null-and-alt-hyp-intercept
exshuffle: TRUE



