```{r data generation, echo = FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
n <- sample(30:100, 1)
# Daily study time (hours)
study_time <- runif(n, min = 0, max = 8)

# True relationship parameters
beta_0 <- 2.0   # baseline GPA
beta_1 <- 0.4   # GPA increase per study hour

# Generate GPA with noise
gpa <- beta_0 + beta_1 * study_time + rnorm(n, mean = 1, sd = 1)

# Keep GPA within 0–7
gpa <- pmin(pmax(gpa, 0), 7)

# Final dataset
data <- data.frame(
  study_time = study_time,
  gpa = gpa
)
data <- round(data,3)
# Fit linear regression model
model <- lm(gpa ~ study_time, data = data)
lala <- summary(model)

rand_hour <- sample(2:8, 1)



choices <- character(4)
choices[1] <- paste0("`confint(model, study_time = ", rand_hour, ")`")
choices[2] <- paste0("`new_data <- data.frame(study_time = ", rand_hour,  ")` \n `predict(model, newdata = new_data)`")
choices[3] <- paste0("`new_data <- data.frame(study_time = ", rand_hour,  ")` \n `predict(model, newdata = new_data, interval = 'prediction')`")
choices[4] <- paste0("`new_data <- data.frame(study_time = ", rand_hour,  ")` \n `predict(model, newdata = new_data, interval = 'confidence')`")

sol <- c(F, F, F, T)


```

Question
===============
A researcher wants to know if daily study time (hours) actually has an effect on students final GPA score (from 0 to 7). They conducted a study with `r n` students, and recorded the students' daily study time and final GPA score. The dataset they collected looks like:
```{r showdata, echo=FALSE}
head(data)
```
The linear regression model is then fitted, the results are shown below:
```{r}
summary(model)
```
Now the researcher wants to know what is the 95% confidence interval for hard-working students that has studied for `r rand_hour` hours. Which R code correctly obtains the 95% confidence interval?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```

Solution
======================
To get the confidence interval, the `predict()` function must be used, where `newdata` must be a data frame, and `interval = "confidence"`. 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: lm-predict-95-CI
exshuffle: TRUE



