```{r data generation, echo = FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
n <- sample(30:100, 1)
# Daily study time (hours)
study_time <- runif(n, min = 0, max = 8)

# True relationship parameters
beta_0 <- 2.0   # baseline GPA
beta_1 <- 0.4   # GPA increase per study hour

# Generate GPA with noise
gpa <- beta_0 + beta_1 * study_time + rnorm(n, mean = 1, sd = 1)

# Keep GPA within 0–7
gpa <- pmin(pmax(gpa, 0), 7)

# Final dataset
data <- data.frame(
  study_time = study_time,
  gpa = gpa
)
data <- round(data,3)
# Fit linear regression model
model <- lm(gpa ~ study_time, data = data)
lala <- summary(model)

rand_hour <- round(runif(n = 1, min = 2, max = 8),3)

newdata <- data.frame(study_time = rand_hour)
conf <- predict(model, newdata = newdata, interval = "confidence")
conf_lb <- conf[2]
conf_ub <- conf[3]

pred <- predict(model, newdata = newdata, interval = "prediction")
pred_lb <- pred[2]
pred_ub <- pred[3]


ques <- round(runif(n = 1, min = 0, max = 7),3)

choices <- character(4)
choices[1] <- "Unusually high"
choices[2] <- "Unusually low"
choices[3] <- "Reasonable"
choices[4] <- "I don't know"

sol <- c(ques >conf_ub, ques < conf_lb, conf_lb<ques & ques <conf_ub, F)


```

Question
===============
A researcher wants to know if daily study time (hours) actually has an effect on students final GPA score (from 0 to 7). They conducted a study with `r n` students, and recorded the students' daily study time and final GPA score. The dataset they collected looks like:
```{r showdata, echo=FALSE}
head(data)
```
The linear regression model is then fitted, the results are shown below:
```{r}
summary(model)
```
Assume that the 95% confidence interval for the mean GPA score when students that studied for `r rand_hour` hours is $$(`r conf_lb`, `r conf_ub`)$$

and the 95% prediction interval for the GPA score when a student that studied for `r rand_hour` hours is $$(`r pred_lb`, `r pred_ub`)$$

Suppose a large group of students who all studied for `r rand_hour` hours per day had an average GPA of `r ques`. How should their GPA be classified?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```

Solution
======================
Because we are evaluating the average GPA of a group of students, the appropriate interval to use is the 95% confidence interval, not the prediction interval. The confidence interval describes plausible values for the mean GPA of all students who studied for `r rand_hour` hours.

The observed average GPA (`r ques`) is
`r ifelse(conf_lb < ques & ques < conf_ub, "within", "outside")` the confidence interval, so the group’s average GPA is classified as: "Reasonable" if it lies within the confidence interval, "Unusually high" if it lies above the upper bound, and "Unusually low" if it lies below the lower bound

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: lm-predict-use-CI-reasonable
exshuffle: TRUE



