```{r data generation, echo = FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
n <- sample(30:100, 1)
# Daily study time (hours)
study_time <- runif(n, min = 0, max = 8)

# True relationship parameters
beta_0 <- 2.0   # baseline GPA
beta_1 <- 0.4   # GPA increase per study hour

# Generate GPA with noise
gpa <- beta_0 + beta_1 * study_time + rnorm(n, mean = 1, sd = 1)

# Keep GPA within 0–7
gpa <- pmin(pmax(gpa, 0), 7)

# Final dataset
data <- data.frame(
  study_time = study_time,
  gpa = gpa
)
data <- round(data,3)

model <- lm(gpa ~ study_time, data = data)
lala <- summary(model)
pval <- lala$coefficients[2,4]

choices <- character(4)
choices[1] <- "Fail to reject the null hypothesis, because the p-value is less than 0.05"
choices[2] <- "Fail to reject the null hypothesis, because the p-value is greater than 0.05"
choices[3] <- "Reject the null hypothesis, because the p-value is less than 0.05"
choices[4] <- "Reject the null hypothesis, because the p-value is greater than 0.05"


sol <- c(F, pval>0.05 , pval<0.05, F)



```

Question
===============
A researcher wants to know if daily study time (hours) actually has an effect on students final GPA score (from 0 to 7). They conducted a study with `r n` students, and recorded the students' daily study time and final GPA score. The dataset they collected looks like:
```{r showdata, echo=FALSE}
head(data)
```
The linear regression model is then fitted, the results are shown below:
```{r}
summary(model)
```
At 5% significance, should we reject or retain the null hypothesis?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```

Solution
======================
The p-value is `r ifelse(pval<0.05, "less than", "greater than")` 0.05, therefore the null hypothesis is `r ifelse(pval<0.05, "rejected", "retained")`
The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: lm-reject-retain-slope
exshuffle: TRUE



