```{r data generation, echo = FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
n <- sample(30:100, 1)
# Daily study time (hours)
study_time <- runif(n, min = 0, max = 8)

# True relationship parameters
beta_0 <- 2.0   # baseline GPA
beta_1 <- 0.4   # GPA increase per study hour

# Generate GPA with noise
gpa <- beta_0 + beta_1 * study_time + rnorm(n, mean = 1, sd = 1)

# Keep GPA within 0–7
gpa <- pmin(pmax(gpa, 0), 7)

# Final dataset
data <- data.frame(
  study_time = study_time,
  gpa = gpa
)
data <- round(data,3)
# Fit linear regression model
model <- lm(gpa ~ study_time, data = data)
lala <- summary(model)
# Get coefficients, std error and t-value
slope <- lala$coefficients[2,1]
slop_se <- lala$coefficients[2,2]
crit_t <- qt(1-0.05/2, df = lala$df[2])
noise <- rnorm(1, mean = 1, sd = 1)

fake_num1 <- round(lala$coefficients[2,1] - crit_t*lala$coefficients[2,2] + abs(noise) ,3) 
fake_num2 <- round(lala$coefficients[2,1] + crit_t*lala$coefficients[2,2] + abs(noise) ,3)


choices <- character(4)
choices[1] <- paste("We are 95% confident that students GPA scores lie between", fake_num1, "and", fake_num2)
choices[2] <- paste("There is a 95% choice that the slope equals to", round((fake_num1 + fake_num2)/2,3))
choices[3] <- paste("We are 95% confident that the true mean increase in GPA score per hour studied is between", fake_num1, "and", fake_num2)
choices[4] <- paste("The slope is either", fake_num1, "or", fake_num2)

sol <- c(F, F, T, F)




```

Question
===============
A researcher wants to know if daily study time (hours) actually has an effect on students final GPA score (from 0 to 7). They conducted a study with `r n` students, and recorded the students' daily study time and final GPA score. The dataset they collected looks like:
```{r showdata, echo=FALSE}
head(data)
```
The linear regression model is then fitted, the results are shown below:
```{r}
summary(model)
```
Assume the 95% CI for the slope is: 
$$`r fake_num1`, `r fake_num2` $$ 


How should this confidence interval be interpreted?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```

Solution
======================
95% confidence interval for the slope describes the range of plausible values for the true mean change in GPA per additional hour of study, not individual GPAs or exact probabilities.

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: lm-slope-interpret-95-CI
exshuffle: TRUE



