```{r data generation, echo = FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
n <- sample(30:100, 1)
# Daily study time (hours)
study_time <- runif(n, min = 0, max = 8)

# True relationship parameters
beta_0 <- 2.0   # baseline GPA
beta_1 <- 0.4   # GPA increase per study hour

# Generate GPA with noise
gpa <- beta_0 + beta_1 * study_time + rnorm(n, mean = 1, sd = 1)

# Keep GPA within 0–7
gpa <- pmin(pmax(gpa, 0), 7)

# Final dataset
data <- data.frame(
  study_time = study_time,
  gpa = gpa
)
data <- round(data,3)

choices <- character(4)

choices[1] <- "two-sample t-test"
choices[2] <- "linear regression"
choices[3] <- "Mann-Whitney U test"
choices[4] <- "ANOVA"

sol <- c(F, T, F, F)
explain <- character(4)
explain[1] <- "Two sample t-test is to test for the effect of 2 groups (categorical) on the mean of numeric data. " 
explain[4] <- "ANOVA is to test the for effect of 3 or more groups (categorical) on the mean of numeric data. "
explain[3] <- "Similar to two sample t-test it is to test if there is a different distribution of the numeric data across 2 different groups. "

```

Question
===============
A researcher wants to know if daily study time (hours) actually has an effect on students final GPA score (from 0 to 7). They conducted a study with `r n` students, and recorded the students' daily study time and final GPA score. The dataset they collected looks like:
```{r showdata, echo=FALSE}
head(data)
```

Which is the appropriate test to see if daily study time has an effect on final GPA score? 
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
======================
The two variables `StudyTime` and `GPA` are both quantitative continuous data (numeric, and can have decimals). Therefore linear regression is the appropriate test for this study. 
The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, explain, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: lm-when-to-use
exshuffle: TRUE



