```{r data generation, echo = FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
n <- sample(30:100, 1)
# Daily study time (hours)
study_time <- runif(n, min = 0, max = 8)

# True relationship parameters
beta_0 <- 2.0   # baseline GPA
beta_1 <- 0.4   # GPA increase per study hour

# Generate GPA with noise
gpa <- beta_0 + beta_1 * study_time + rnorm(n, mean = 1, sd = 1)

# Keep GPA within 0–7
gpa <- pmin(pmax(gpa, 0), 7)

# Final dataset
data <- data.frame(
  study_time = study_time,
  gpa = gpa
)
data <- round(data,3)
choices <- character(4)

choices[1] <- "`lm(gpa ~ study_time, data = data)`"
choices[2] <- "`lm(study_time ~ gpa, data = data)`"
choices[3] <- "`t.test(gpa ~ study_time, data = data)`"
choices[4] <- "`lm(data$gpa - data$study_time)`"

sol <- c(T, F, F, F)

```

Question
===============
A researcher wants to know if daily study time (hours) actually has an effect on students final GPA score (from 0 to 7). They conducted a study with `r n` students, and recorded the students' daily study time and final GPA score. The dataset they collected looks like:
```{r showdata, echo=FALSE}
head(data)
```

Which R command correctly fits a simple linear regression model that predicts exam score from study hours?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```

Solution
======================
The response variable is gpa score, and the predictor variable is study hours. 
To fit a linear model in R, the code to use is `lm(response ~ predictor, data = dataset)`.
The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: lm-which-code-to-use
exshuffle: TRUE



