```{r data generation, echo = FALSE, results='hide'}
pacman::p_load(tidyverse, exams)
n <- sample(30:100, 1)
# Daily study time (hours)
study_time <- runif(n, min = 0, max = 8)

# True relationship parameters
beta_0 <- 2.0   # baseline GPA
beta_1 <- 0.4   # GPA increase per study hour

# Generate GPA with noise
gpa <- beta_0 + beta_1 * study_time + rnorm(n, mean = 1, sd = 1)

# Keep GPA within 0–7
gpa <- pmin(pmax(gpa, 0), 7)

# Final dataset
data <- data.frame(
  study_time = study_time,
  gpa = gpa
)
data <- round(data,3)
choices <- character(4)

choices[1] <- "`plot(model)`"
choices[2] <- "`summary(model)`"
choices[3] <- "`predict(model)`"
choices[4] <- "`residuals(model)`"
sol <- c(T, F, F, F)

```

Question
===============
A researcher wants to know if daily study time (hours) actually has an effect on students final GPA score (from 0 to 7). They conducted a study with `r n` students, and recorded the students' daily study time and final GPA score. The dataset they collected looks like:
```{r showdata, echo=FALSE}
head(data)
```
Let `model` be the linear regression model fitted in R,  which command produces standard diagnostic plots for checking regression assumptions?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```

Solution
======================
`plot(model)` produces the 4 diagnostic plots for the assumptions of the linear regression. 
The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```

Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: lm-which-code-to-use-diagnostic-plots
exshuffle: TRUE



