```{r data generation, echo=FALSE, results='hide'}
num_dogs <- sample(20:30, 1)

# Dog owners: mostly unbothered
dog_judgment <- sample(
  x = 1:6,
  size = num_dogs,
  replace = TRUE,
  prob = c(0.10, 0.25, 0.30, 0.20, 0.10, 0.05)
)

# Cat owners: deeply judged
cat_judgment <- sample(
  x = 3:10,
  size = num_dogs,
  replace = TRUE,
  prob = c(0.05, 0.05, 0.10, 0.15, 0.20, 0.20, 0.15, 0.10)
)

data <- data.frame(
  dog_judgment = dog_judgment,
  cat_judgment = cat_judgment
)

mytest <- wilcox.test(data$dog_judgment, data$cat_judgment, exact = FALSE)
choices <- character(4)
choices[1] <- "There is a statistically significant difference in the distribution of judgement between cats and dogs"
choices[2] <- "There is no statistically significant difference in the distribution of judgement between cats and dogs"
choices[3] <- "There is a statistically significant difference in the means of the judgement score between cats and dogs"
choices[4] <- "There is no statistically significant difference in the means of the judgement score between cats and dogs"
sol <- c(mytest$p.value < 0.05, mytest$p.value>0.05, F, F)


explain <- ifelse(mytest$p.value < 0.05, "The p-value of the Mann Whitney U test is less than 0.05, therefore the null hypothesis is rejected. That means that there is a statistically significant difference in distribution of the two groups.", "The p-value of the Mann Whitney U test is greater than 0.05, therefore the null hypothesis is retained. That means that a there is insufficient evidence to prove that there is a statistically significant difference in distribution of the two groups.")

```

Question
===================
A behavioural science lab wants to study perceived judgement from pets. They recruit pet owners and ask them to rate, on a 1-10 scale, how judged the owners feel when their pet watches them eat dropped food from the floor. This dataset collected has 2 variables:

1.  Scale of judgement:
1 = "pure unconditional love"
10 = "you have severely disrespected my ancestors" 

2.  Type of pets: dogs and cats

The final dataset looks like:
```{r show data, echo=FALSE}
head(data)
```

A Mann Whitney U test was used in this study, the output is shown below:
```{r show ouput, echo = FALSE}
mytest
```
Which is the correct interpretation at the 5% significance level?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```




Solution
======================
`r explain`

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```




Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: mann-whitney-interpret-results
exshuffle: TRUE


