```{r}
choices <- character(4)
choices[1] <- "The before-treatment scores must be normally distributed"
choices[2] <- "The after-treatment scores must be normally distributed"
choices[3] <- "The change scores (after – before) must be normally distributed"
choices[4] <- "Both distributions must be symmetric"


sol <- c(FALSE,FALSE,TRUE,FALSE)
```

Question
=====================
A researcher measures blood pressure before and after a treatment on the same subjects. For the matched-pairs t-test to be valid, which condition must hold?

```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```


Solution
===================
Normality must apply only to the differences, not each raw distribution separately.


The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```




Meta-information
================
exname: matched-pairs-t-test-assumptions-2
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE
