```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)
choices[1] <- "The differences between paired observations are approximately normally distributed"
choices[2] <- "The pairs are meaningfully matched"
choices[3] <- "Each group must have the same variance"
choices[4] <- "The pairs are randomly sampled"


sol <- c(FALSE,FALSE,TRUE,FALSE)
```


Question
=============
Which of the following is not an assumption of a matched pairs t-test?

```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```



Solution
=================
The matched-pairs test analyses differences, so equal variances between groups is irrelevant. What matters is normality of differences, proper pairing, and random sampling.

The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```




Meta-information
================
exname: matched-pairs-t-test-assumptions
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE
