```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(exams, tidyverse)
# Set random seed for reproducibility
set.seed(123)

# Number of paired observations
n <- 30

# Generate random data for the Control and Treatment groups
# Assume the Control group has a mean of 120 with a standard deviation of 10
# Assume the Treatment group has a mean of 122 with a standard deviation of 10
control <- rnorm(n, mean = 120, sd = 10)
treatment <- rnorm(n, mean = 122, sd = 10)

# Calculate the differences between Treatment and Control for each pair
differences <- treatment - control

# Perform the paired t-test
t_test_result <- t.test(differences)

# Extract the confidence interval from the t-test result
lower <- t_test_result$conf.int[1]
upper <- t_test_result$conf.int[2]


choices <- character(4)
explain <- character(4)

choices[1] <- "The treatment definitely has no effect."
choices[2] <-  "There is evidence that Treatment increases blood pressure."
choices[3] <- "The treatment effect could be negative, zero, or positive based on this interval."
choices[4] <- paste("95% of patients had blood pressure changes between", round(lower,2) , "and", round(upper,2), "mmHg")

sol <- c(FALSE,FALSE,TRUE,FALSE)
```

Question
==================
A researcher performs a matched pairs t-test to compare blood pressure changes between a Treatment group and a Control group. The results of the test is shown below


```{r printresult, echo = FALSE, results='markup'}
print(t_test_result)
```

Based on the 95% Confidence Interval, what conclusion is the most reasonable?
```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```


Solution
==============
Because the confidence interval includes zero, this suggests that the data are consistent with the possibility that the treatment has no effect, or could have either a negative or positive effect. It does not provide strong evidence for a significant difference. The statement about 95% of individual blood pressure changes is not relevant to the interpretation of a confidence interval for the mean difference.

The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```




Meta-information
================
exname: matched-pairs-t-test-CI-interpret
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE
