```{r data generation, echo=FALSE, results='hide'}
num_samples <- sample(35:100, 1)
choices <- character(4)
ques <- sample(1:5, 1)
ques_s <- ques*60

sigma <- 20
data <- data.frame(
  duration = rnorm(
    n = num_samples,
    mean = ques_s + 15,  # teachers run long
    sd = sigma)
  )
data$duration <- round(data$duration,1)

my_ttest <- t.test(data$duration, mu = ques_s)
p_val <- my_ttest$p.value


choices <- character(4)

choices[1] <- "Fail to reject the null hypothesis"
choices[2] <- "Reject the null hypothesis"
choices[3] <- "Accept the null hypothesis"
choices[4] <- "The result is inconclusive"


sol <- c(p_val > 0.05, p_val<0.05, F, F)
explain <- character(4)
explain[1] <- ifelse(p_val>0.05, " ", "The p-value is greater than 0.05, therefore we fail to reject the null hypothesis at the 5% significance level. In other words, we retain the null hypothesis at the 5% significance level.")
explain[2] <- ifelse(p_val<0.05, " ", "The p-value is greater than 0.05, therefore we reject the null hypothesis at the 5% significance level.")
explain[3] <- "The null hypothesis cannot be accepted, as statistical tests only provide evidence against it, not definitive proof for it. "

explain[4] <- "Once a significance level is chosen, a hypothesis test always leads to a decision: reject or fail to reject the null hypothesis. Therefore, 'the result is inconclusive' is not a valid conclusion."




```



Question
=================
At the end of class, teachers sometimes announce that they “just have a few things to go through” and reassure students by saying, “This will only be `r ques` minutes.” 

To test whether this claim is accurate, a student recorded the duration (in seconds) of `r num_samples` randomly selected end-of-class announcements in which teachers explicitly stated, “This will only be `r ques` minutes.”

The data recorded is shown below:
```{r showdata, echo = TRUE}
head(data)
```


The one-sample t-test is then ran, the output is then shown below:
```{r showoutput, echo=FALSE, results='asis'}
print(my_ttest)
```

At the 5% significance level, which is the correct conclusion?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
================
The t-statistic measures how many standard errors the sample mean is away from the hypothesised mean.

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, explain, markup = "markdown")
```




Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol)`
exname: one-sample-t-test-conclusion
exshuffle: TRUE

