```{r data generation, echo=FALSE, results='hide'}
num_samples <- sample(35:100, 1)
choices <- character(4)
ques <- sample(1:5, 1)
ques_s <- ques*60

sigma <- 20
data <- data.frame(
  duration = rnorm(
    n = num_samples,
    mean = ques_s + 15,  # teachers run long
    sd = sigma)
  )
data$duration <- round(data$duration,1)

choices[1] <- paste0("`t.test(data$duration, mu = ", ques_s,")`")
choices[2] <- paste0("`t.test(duration = ", ques_s, ") `")
choices[3] <- paste0("`t.test(duration ~ ", ques_s,")`")
choices[4] <- paste0("`t.test(mean(data$duration), mu =  ", ques_s,")`")
sol <- c(T,F,F,F)
```



Question
=================
At the end of class, teachers sometimes announce that they “just have a few things to go through” and reassure students by saying, “This will only be `r ques` minutes.” 

To test whether this claim is accurate, a student recorded the duration (in seconds) of `r num_samples` randomly selected end-of-class announcements in which teachers explicitly stated, “This will only be `r ques` minutes.”
The data recorded is shown below:
```{r showdata, echo = TRUE}
head(data)
```


Which R code correctly performs the one-sample t-test?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
================

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```




Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: one-sample-t-test-correct-code
exshuffle: TRUE

