```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)

choices[1] <- "The population mean must be known"
choices[2] <- "The sample must come from a normally distributed population (or large enough $n$)"
choices[3] <- "The population variance must be known"
choices[4] <- "The sample must be divided into two groups"

sol <- c(FALSE, TRUE, FALSE, FALSE)

```


Question 
================
The one sample t-test requires:

```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```





Solution 
==================
The one-sample t-test assumes the underlying population is approximately normal or $n$ is large (via the Central Limit Theorem). Population parameters do not need to be known. 


The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```


Meta-information
================
exname: one-sample-t-test-assumption
extype: schoice
exshuffle: TRUE
exsolution: `r mchoice2string(sol, single = TRUE)`
