```{r data generation}
num <- sample(30:60, 1)
avg <- sample(2:10, 1)
sd <- sample(1:5, 1)
lb <- round((avg)-2.064*sd/sqrt(num),3)
ub <- round((avg)+2.064*sd/sqrt(num),3)

choices <- character(4)
choices[1] <- paste0("Retain the null hypothesis because ", avg, " is contained within the 95% confidence interval")
choices[2] <- paste0("Reject the null hypothesis, because ", avg, " is not in the 95% confidece interval")
choices[3] <- paste0("Cannot make a conclusion without the p-value")
choices[4] <- paste0("Retain the null hypothesis because the interval is wide")

sol <- c(avg>lb & avg<ub, avg<lb|avg>ub, F, F)

```


Question
===================
A city park claims that on average, squirrels steal `r avg` donuts per day from picnickers.

A group of researchers decides to test this claim. For `r num` days, they secretly observe donut thefts and record how many donuts disappear each day stolen by squirrels.

The 95% confidence interval these researchers calculated is:
$$(`r lb`, `r ub`)$$

What is the corret conclusion at the 5% significance level?
```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
================
The null and alternative hypotheses for this test are:
$$H_0: \mu = `r avg`$$
$$H_a: \mu \neq `r avg`$$
The hypothesised value is contained within the confidence interval, therefore the null hypothesis is retained at the 5% significance level.
The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```




Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol)`
exname: one-sample-t-test-reject-or-retain-using-CI
exshuffle: TRUE



