```{r data generation, echo=FALSE, results='hide'}
num_samples <- sample(35:100, 1)
choices <- character(8)
ques <- sample(1:5, 1)
ques_s <- ques*60

sigma <- 20
data <- data.frame(
  duration = rnorm(
    n = num_samples,
    mean = ques_s + 15,  # teachers run long
    sd = sigma)
  )
data$duration <- round(data$duration,1)




choices[1] <- paste0("$H_0: \\mu =",  ques_s,"$")
choices[2] <- paste0("$H_a: \\mu \\neq", ques_s, "$")
choices[3] <- paste0("$H_a: \\mu =", ques_s, "$")
choices[4] <- paste0("$H_0: \\mu \\neq",ques_s,"$")
choices[5] <- paste0("$H_0: \\mu \\geq" , ques_s,"$")
choices[6] <- paste0("$H_a: \\mu <",  ques_s,"$")
choices[7] <- paste0("$H_0: \\mu \\leq", ques_s, "$")
choices[8] <- paste0("$H_a: \\mu > ", ques_s, "$")

sol <- c(T,T, F, F, F, F, F, F)
```



Question
=================
At the end of class, teachers sometimes announce that they “just have a few things to go through” and reassure students by saying, “This will only be `r ques` minutes.” 

To test whether this claim is accurate, a student recorded the duration (in seconds) of `r num_samples` randomly selected end-of-class announcements in which teachers explicitly stated, “This will only be `r ques` minutes.”

The data recorded is shown below:
```{r showdata, echo = TRUE}
head(data)
```


Which are the appropriate null and alternative hypotheses to test if “This will only be `r ques` minutes.” is actually `r ques_s` seconds (`r ques` minutes)?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
================
The appropriate null and alternative hypotheses are:
$$H_0: \mu = `r ques_s`$$
$$H_a: \mu \neq `r ques_s`$$

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```




Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol)`
exname: one-sample-t-test-null-and-alt
exshuffle: TRUE

