```{r data generation, echo=FALSE, results='hide'}
num_samples <- sample(35:100, 1)
choices <- character(4)
ques <- sample(1:5, 1)
ques_s <- ques*60

sigma <- 20
data <- data.frame(
  duration = rnorm(
    n = num_samples,
    mean = ques_s + 15,  # teachers run long
    sd = sigma)
  )
data$duration <- round(data$duration,1)

my_ttest <- t.test(data$duration, mu = ques_s)
ci_lb <- round(my_ttest$conf.int[1],2)
ci_ub <- round(my_ttest$conf.int[2],2)


choices <- character(4)
choices[1] <- paste0(
  "95% of teachers use between ", ci_lb, " and ", ci_ub,
  " seconds when they say they will only be ", ques, " minutes."
)

choices[2] <- paste0(
  "There is a 95% probability that the true mean duration is between ",
  ci_lb, " and ", ci_ub,
  " seconds when teachers say they will only be ", ques, " minutes."
)

choices[3] <- paste0(
  "We are 95% confident that the true mean duration is between ",
  ci_lb, " and ", ci_ub,
  " seconds when teachers say they will only be ", ques, " minutes."
)

choices[4] <- paste0(
  "The sample mean lies between ", ci_lb, " and ", ci_ub,
  " seconds with probability 0.95."
)

sol <- c(F, F, T, F)

explain <- character(4)

explain[1] <- 
  "Confidence interval describes uncertainty about the population mean, not the proportion of individual teachers."

explain[2] <- 
  "The true mean is a fixed (but unknown) value. The 95% refers to the long-run success rate of the method, not the probability that the true mean lies in this specific interval."


explain[4] <- 
  "The sample mean is a fixed value once the data are collected. The probability statement applies to the confidence interval procedure, not to the observed sample mean."



```



Question
=================
At the end of class, teachers sometimes announce that they “just have a few things to go through” and reassure students by saying, “This will only be `r ques` minutes.” 

To test whether this claim is accurate, a student recorded the duration (in seconds) of `r num_samples` randomly selected end-of-class announcements in which teachers explicitly stated, “This will only be `r ques` minutes.”

The data recorded is shown below:
```{r showdata, echo = TRUE}
head(data)
```


The one-sample t-test is then ran, the output is then shown below:
```{r showoutput, echo=FALSE, results='asis'}
print(my_ttest)
```

Which interpretation is correct about the 95% confidence interval?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
================
The confidence level is interpreted by:
We are `CI level` confident that the true `parameter` of `population` lies between `lower` and `upper` `units`. 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, explain, markup = "markdown")
```




Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol)`
exname: one-sample-t-test-95-ci-interpret
exshuffle: TRUE

