```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)

choices[1] <- "Only the 200 sampled households."
choices[2] <- "All households in the city."
choices[3] <- "All households in the country."
choices[4] <- "Any population of households with similar demographics."


sol <- c(FALSE,TRUE,FALSE,FALSE)

```



Question
=====================
A researcher samples 200 households using simple random sampling from a city of 50,000 households. To which population can the resulting confidence interval for mean household income be generalised?


```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```




Solution
================
With simple random sampling from the city population, the inference generalises to that same population. It cannot automatically generalise to larger or unrelated populations.

The correct answer is:

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```



Meta-information
================
exname: population-CI-generalises-to
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE
