```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)

choices[1] <- "The CI can be generalised to all students in Adelaide University."
choices[2] <- "The CI can be generalised to all university students in Australia."
choices[3] <- "The CI can only be applied to the 30 sampled students."
choices[4] <- "The CI applies only if the data are normally distributed."


sol <- c(TRUE,FALSE,FALSE,FALSE)

```


Question
==================
Researchers randomly select 30 students from Adelaide University to estimate mean study hours. Which statement is true?


```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```




Solution
====================
Random sampling from a well-defined population (students at the university) allows valid inference to that population. There is no justification for generalising to all university students elsewhere.

The correct answer is:

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```

Meta-information
================
exname: population-CI-generalises-to-2
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exshuffle: TRUE

