```{r data generation, echo=FALSE, results='hide'}
choices <- character(8)
sol <- logical(length(choices))
choices[1] <- "Rows: Variables" 
choices[2] <- "Columns: Subjects"
choices[3] <- "Rows: Subjects"
sol[3] <- TRUE
choices[4] <- "Columns: Variables"
sol[4] <- TRUE
choices[5] <- "Rows: Measurements"
choices[6] <- "Columns: Experiments"
choices[7] <- "Rows: Categories"
choices[8] <- "Columns: Outcomes"


```
Question
===============
A dataset has 365 rows and 3 columns. Each row represents one day, and each column represents a different weather measurement (temperature, rainfall, windspeed). 


What do the rows and the columns represent?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
==============
In rectangular data, rows correspond to subjects and columns to variables.

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(sol)`
exname: rectangular-data-interpretation
exshuffle: TRUE
