```{r data generation, echo = FALSE, results='hide'}
error <- sample(c(1:7),1)

choices <- character(4)
choices[1] <- "The thermometer is valid but not reliable"
choices[2] <- "The thermometer is reliable but not valid"
choices[3] <- "The thermometer is neither reliable nor valid"
choices[4] <- "The thermometer is both reliable and valid"

sol <- c(FALSE, TRUE, FALSE, FALSE)
```


Question
============
A thermometer gives nearly identical readins each time it is used, but all readings are consistently `r error`$^o$C higher than the true temperature. 
Which of these statements is correct?
```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```


Solution
=================
Consistency implies reliability, but systematic error reduces validity. 

The correct answer is 
```{r answerlist, echo=FALSE, results='asis'}
answerlist(sol, markup = "markdown")
```



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(correct, single = TRUE)`
exname: reliability-vs-validity



