```{r data generation, echo = FALSE, results = "hide"}
pacman::p_load(tidyverse, exams)
sample <- sample(0:100, 14, replace = TRUE)
sample <- round(sample,0)
length <- length(sample)
sorted <- sort(sample)
sol <- round(IQR(sample),1)
median <- median(sample)
Q1 <- quantile(sample, probs = 0.25) %>% as.numeric()
Q3 <- quantile(sample, probs = 0.75) %>% as.numeric()


list_of_answers <- c(sol, Q1, Q3, median(sample))
list_of_correct <- c(TRUE, FALSE, FALSE, FALSE)

order_of_questions <- sample.int(4,4,replace = FALSE)

list_of_answers <- list_of_answers[order_of_questions]

list_of_correct <- list_of_correct[order_of_questions]
# Q3-Q1
```

Question 
==============

What is the interquartile range of the following sample:

$`r sample`$

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(list_of_answers)
```


Solution
=================

The interquartile range of the sample is:

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(list_of_correct, "TRUE", "FALSE"), markup = "markdown")
```

<br>
<br>
The interquartile range is calculated by taking the difference of the third quartile and first quartile. 

First order the samples from low to high 

$$`r sorted`$$


then take the median (central number).<br>

<br>
The first quartile is the median of the lower half of the numbers (all the numbers below the median):
<br>
$$`r sorted[1:(length(sample)/2)]`$$
<br>
and the third quartile is the median of the upper half of the numbers(the numbers above the overall median):
<br>

$$ `r sorted[(length(sample)/2+1):length(sample)]`$$
<br>

In R, the data can be entered using:
<br>
```{r, echo = FALSE}
cat('sample=c(',paste(sample, collapse=','), ')\n', sep = '')

```

<br>
Then you can compute the interquartile range (IQR) like so:
<br>
```{r}
IQR(sample)
```
<br>
which rounded to one decimal place is `r sol`.

Meta-information
================

extype: schoice
exsolution: `r mchoice2string(list_of_correct, single = TRUE)`
exname: calculate iqr
