```{r data generation, echo=FALSE, results='hide'}
# Data generation 
n <- 40 + sample(1:12, 2) *3

# queue
waiting <- rnorm(sum(n), sd = sample(30:40,1)/10 + rep(sample(30:80, 2)/10), n)
waiting[waiting < 0 ] <- 0

df <- data.frame(
  waiting = waiting,
  supermarket = factor(rep(1:2, c(n[1], n[2])), levels = 1:2, c("Foodland", "Aldi"))
)


tt <- t.test(data = df, waiting~supermarket, var.equal = TRUE, alternative = sample(c("less", "greater", "two.sided"),1))

list_of_ans <- c("True", "False")

list_of_ans <- c("True", "False")
if (tt$statistic>1.96){
  sol <- c(TRUE, FALSE)
} else sol <- c(FALSE, TRUE)



```

Question
==============

The waiting time (in minutes) at the self-checkout of two suprermarket chains is compared. The following statistical test was performed:

```{r test output, echo=FALSE, comment=NA}
print(tt)
```

From the output above, is this statement correct?:

"The absolute value of the test statistic is greater than 1.96."

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(list_of_ans,  markup = "markdown")
```


Solution
=================

```{r solutionlist, echo=FALSE, results='asis'}
answerlist(ifelse(sol, "True", "False"), markup = "markdown")
```

The test-statistic can be found by looking at the `` t = `r round(tt$statistic, 5)` ``

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: read test statistic 2sample ttest

