```{r data generation, echo=FALSE, results='hide'}
num_trials <- sample(c(20:100), size = 1)
num_success <- round(sample(seq(from = 0.5, to = 0.9, by = 0.05), size = 1) * num_trials,0)

choices <- character(4)
choices[1] <- "The coin is definitely biased."
choices[2] <- "The coin is fair because randomness explains everything."
choices[3] <- "The results suggests possible bias, but chance variation is plausible."
choices[4] <- "The experiment is invalid because randomness was involved."


sol <- c(FALSE, FALSE, TRUE, FALSE)
```

Question
================
A coin is flipped `r num_trials` time, and `r num_success` heads are observed. 
Which conclusion best reflects the appropriate scientific reasoning?

```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```


Solution
==================
Scientific conclusion should acknowledge random variation and avoid abslute claims based on a single experiment. 

The correct answer is
```{r answerlist, echo=FALSE, results='asis'}
answerlist(sol, markup = "markdown")

```



Meta-information
================
exname: scientific-reasoning-coin
exshuffle: TRUE
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`

