```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)
choices[1] <- "The two sample sazes have different means"
choices[2] <- "The sample sizes of the two groups are identical"
choices[3] <- "Each observation in Group A corresponds naturally to one in Group B"
choices[4] <- "The data are normally distributed within each group"


sol <- c(FALSE, FALSE, TRUE, FALSE)
```

Question
===============
A student is unsure whether to use a matched-pairs t-test or a two-sample-t-test. Which clue indicates the matched-pairs t-test is appropriate?
```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```



Solution
================
Matched pairs t-tests are used when observations are linked/paired.

The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```






Meta-information
================
exname: t-test-combined-concepts2
exshuffle: TRUE
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`

