```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)
choices[1] <- "One-sample t-test"
choices[2] <- "Two-sample t-test"
choices[3] <- "Matched-pairs t-test"
choices[4] <- "None of the above"


sol <- c(FALSE, FALSE, TRUE, FALSE)
```

Question
===============
Which of the following t-tests requires independence within groups but NOT between groups?
```{r questionlist, echo=FALSE, results='asis'}
answerlist(choices, markup = "markdown")
```



Solution
================
In paired test, observations within a pair are not independent, but the pairs themselves must be independent of one another. The other tests require full independence of observation within and across groups (where applicable).


The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```






Meta-information
================
exname: t-test-combined-concepts
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`

