```{r data generation, echo=FALSE, results='hide'}
choices <- character(4)

choices[1] <- "Samples are independent within groups"
choices[2] <- "Samples are independent across group"
choices[3] <- "Samples are normally distributed within groups"
choices[4] <- "Samples are normally distributed across groups"

sol <- c(FALSE, FALSE, FALSE,TRUE)


```


Question
=============
Which assumption is not necessary for a two-sample t-test?

```{r questionlist, echo=FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```



Solution
================
The assumptions for a two-sample t-test are 
-  Independence within and across groups, and 
-  Data are normally distributed within each group. 

The correct answer is

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "TRUE", "FALSE"), markup = "markdown")
```



Meta-information
================
exname: two-sample-t-test-assumption
extype: schoice
exshuffle: TRUE
exsolution: `r mchoice2string(sol, single = TRUE)`