```{r data generation, echo=FALSE, results='hide'}
pacman::p_load(exams, tidyverse)

choices <- c("Categorical ordinal", "Categorical nominal", "Quantitative discrete", "Quantitative continuous")
question <- character(16)
solution <- character(16)
explain <- character(16)

question[2] <- "The suburb of residence of people attending the Royal Adelaide Show."
solution[2] <- choices[2]


question[3] <- "The number of koalas counted in Cleland Wildlife Park."
solution[3] <- choices[3]


question[4] <- "The amount of milk (in litres) sold at a Foodland supermarket per day."
solution[4] <- choices[4]

question[5] <- "The satisfaction rating in a student survey (Very Unsatisfied, Unsatisfied, Neutral, Satisfied, Very Satisfied)."
solution[5] <- choices[1]


question[6] <- "The brand of breakfast cereal chosen by Woolworths customers."
solution[6] <- choices[2]


question[7] <- "The number of tram stops between Glenelg and the Adelaide city centre."
solution[7] <- choices[3]


question[8] <- "The length (in centimetres) of barramundi caught by fishers in the Murray River."
solution[8] <- choices[4]


question[9] <- "The star rating (1–5 stars) given by movie-goers at the Palace Nova cinema."
solution[9] <- choices[1]



question[10] <- "The blood type (A, B, AB, O) of donors at the Australian Red Cross Lifeblood centre."
solution[10] <- choices[2]


question[11] <- "The number of siblings a university student has."
solution[11] <- choices[3]


question[12] <- "The weight (in kilograms) of luggage checked in at Adelaide Airport."
solution[12] <- choices[4]

question[13] <- "The ranking of tennis players in the Australian Open (1st, 2nd, 3rd, etc.)."
solution[13] <- choices[1]


question[14] <- "The colour of beach towels seen at Semaphore Beach."
solution[14] <- choices[2]

question[15] <- "The number of AFL premierships won by Port Adelaide."
solution[15] <- choices[3]


question[16] <- "The satisfaction level with train punctuality (Poor, Fair, Good, Very Good, Excellent)."
solution[16] <- choices[1]


random <- sample(1:16,1)

sol <- ifelse(choices == solution[random], TRUE, FALSE)


```



Question 
==================
For the following data collected by a very hardworking scientist doing research, state whether the variable is categorical nominal, categorical ordinal, quantitative discrete, or quantitative continuous.

`r question[random]`



```{r questionlist, echo = FALSE, results = "asis"}
answerlist(list_of_ans,  markup = "markdown")
```


Solution
===========================


```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(ifelse(sol, "True", "False"), markup = "markdown")
```







Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single = TRUE)`
exname: what is the best plot penguins 
