```{r data generation, echo=FALSE, results='hide'}
rand_mean <- sample(200:300, 1)
rand_var <- sample(15:30, 1)
rand_question <- sample(250:450,1)


choices <- character(4)

choices[1] <- paste0("`rnorm(", rand_question, ", mean = ", rand_mean, ", sd = ", rand_var , ")`")
choices[2] <- paste0("`qnorm(", rand_question, ", mean = ", rand_mean, ", sd = ", rand_var , ")`")
choices[3] <- paste0("`dnorm(", rand_question, ", mean = ", rand_mean, ", sd = ", rand_var , ")`")
choices[4] <- paste0("`pnorm(", rand_question, ", mean = ", rand_mean, ", sd = ", rand_var , ")`")

sol <- c(FALSE,FALSE,FALSE,TRUE)
```

Question
==============
The time for a plant its first flower to bloom is normally distributed with mean `r rand_mean` days and a standard deviation of `r rand_var` days. 
Which R command computes the probability that a randomly selected plant takes less than `r rand_question` days for its first flower to bloom?


```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```




Solution
=======================
`pnorm()` computes the cumulative distribution, $P(X \leq x)$

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```


Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single=TRUE)`
exname: which-norm-to-use-pnorm
exshuffle: TRUE


