```{r data generation, results='hide', echo=FALSE}
data <- data.frame(student_id = 1:120, 
                   hours_studied = abs(rnorm(120, mean=5, sd = 3)),
                   exam_score = rgamma(120, shape =20 , scale=2))

choices <- character(4)
choices[1] <- "`data %>% ggplot(aes(x = hours_studied, y = exam_score)) + geom_point()`"
choices[2] <- "`data %>% ggplot(aes(x = hours_studied, y = exam_score)) + geom_boxplot()  `"
choices[3] <- "`data %>% ggplot(aes(x = exam_score)) + geom_boxplot()`"
choices[4] <- "`data %>% ggplot(aes(x = hours_studied)) + geom_histogram()`"

sol <- c(TRUE, FALSE,FALSE,FALSE)

```

Question
====================
A scientist thinks that if a student studies for longer hours, they will have better scores in their exams. The scientist ran an experiment and recorded the data shown below for 120 students:
```{r showdata}
head(data)
```

Which R command is the most appropriate to visualise this relationship?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
==============
A scatterplot (`geom_point()`) is used to visualise relationships between two numeric variables. 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single=TRUE)`
exname: which-plot-is-best-to-use-2-var
exshuffle: TRUE
