```{r data generation, results='hide', echo=FALSE}
base_data <- rnorm(120, mean=0.6, sd = 0.1)
noise <- rgamma(120, shape =0.1 , scale=0.01)
data <- data.frame(id = 1:120 ,reaction_time = base_data-noise)

choices <- character(4)
choices[1] <- "`data %>% ggplot(aes(x = reaction_time)) + geom_histogram()`"
choices[2] <- "`data %>% ggplot(aes(x = reaction_time)) + geom_bar()`"
choices[3] <- "`data %>% ggplot(aes(x = id, y = reaction_time)) + geom_point()`"
choices[4] <- "`data %>% ggplot(aes(x = reaction_time, y = id)) + geom_boxplot()`"

sol <- c(TRUE, FALSE,FALSE,FALSE)

```

Question
====================
you have a numeric variable, `reaction_time`, measured for 120 participants:
```{r showdata}
head(data)
```

Which R command is the most appropriate to visualise its distribution?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(choices,  markup = "markdown")
```



Solution
==============
A histogram is appropriate for visualising the distribution of a single numeric variable. 

The correct answer is 
```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(sol, markup = "markdown")
```





Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sol, single=TRUE)`
exname: which-plot-is-best-to-use-1-var
exshuffle: TRUE
